---
title: "DPLYR penguins"
format: html
editor: visual
---

```{r}
library(tidyverse)
library(palmerpenguins)
library(here)
library(janitor)
```

```{r}
penguins <- read_csv(here("data/penguins_lter.csv"))
```

```{r}
penguins <- palmerpenguins::penguins
```

## 3. Filter()

####  **Practice Activity 1**

Use `filter()` to create a subset from `penguins` that only contains gentoo penguins with a bill depth greater than or equal to 15.5 millimeters.

```{r}
gentoo_penguins_long_bill <- penguins %>%
  filter(species == "Gentoo", bill_depth_mm >= 15.5)
```

```{r}
ggplot(gentoo_penguins_long_bill, aes(x= bill_depth_mm, y = bill_length_mm, fill = bill_depth_mm)) +
  geom_bar(stat = "identity")
```

####  **Practice Activity 2**

Use `filter()` to create a subset from `penguins` that contains observations for male penguins recorded at Dream and Biscoe Islands.

```{r}
penguins %>%
  filter(sex == "male", island == "Dream" | island == "Biscoe")
```

####  **Practice Activity 3**

Use `filter()` to create a subset from `penguins` that contains observations for female Adelie penguins with bill lengths less than 35 mm.

```{r}
penguins %>%
  filter(species == "Adelie", sex == "female", bill_length_mm < 35)
```

####  **Practice Activity 4**

Create a subset from `penguins` containing observations for female chinstrap penguins on Dream and Torgersen Islands.

```{r}
penguins %>%
  filter(species == "Chinstrap", sex == "female", island == "Dream" | island == "Torgersen")

```

####  **Practice Activity 5**

Create a subset from `penguins` that contains penguins that are either gentoos **OR** have a body mass greater than 4500 g.

```{r}
large_gentoos <- penguins %>%
  filter(species == "Gentoo" | body_mass_g > 4500)
```

```{r}
min(large_gentoos$body_mass_g, na.rm = TRUE)
```

## 4. Select()

####  **Practice Activity 1**

Starting with the `penguins` data, only keep the `body_mass_g` variable.

```{r}
penguins %>%
  select(body_mass_g)
```

####  **Practice Activity 2**

Starting with the `penguins` data, keep columns from `bill_length_mm` to `body_mass_g`, and `year`

```{r}
penguins %>%
  select(bill_length_mm:body_mass_g, year)
```

####  **Practice Activity 3**

Starting with the `penguins` data, keep all columns except `island`

```{r}
penguins %>%
  select(-island)
```

####  **Practice Activity 4**

From `penguins`, keep all variables *except* `species`, `sex` and `year`.

```{r}
penguins %>%
  select(!c(species, sex, year))
```

####  **Practice Activity 5**

From `penguins`, keep the `species` column and any columns that end with “mm”.

```{r}
penguins %>%
  select(species, ends_with("mm"))
```

####  **Practice Activity 6**

From `penguins`, keep any columns that contain “bill” OR end with “mm”.

```{r}
penguins %>%
  select(ends_with("mm") | contains("bill"))
```

#### **Practice Activity 7**

In a piped sequence, starting from `penguins`:

-   Only keep observations for female penguins observed on Dream Island, THEN…

-   Keep variables `species`, and any variable starting with “bill”

```{r}
penguins %>%
  filter(sex == "female", island == "Dream") %>%
  select(species, starts_with("bill"))
```

## 5. Relocate()

####  **Practice Activity 1**

Starting with `penguins`, move the `species` variable to before the `sex` variable.

```{r}
penguins %>%
  relocate(species, .before = sex)
```

####  **Practice Activity 2**

Starting with `penguins`, relocate the `bill_length_mm` variable so that it is the first column.

```{r}
penguins %>%
  relocate(bill_length_mm)
```

####  **Practice Activity 3**

Move any factor variables (hint: `is.factor`) to after any integer variables (`is.integer`).

```{r}
penguins %>%
  relocate(where(is.factor), .after = where(is.integer))
```

## 6. Rename()

####  **Practice Activity 1**

Starting with `penguins`, rename the `flipper_length_mm` column to `flipper_mm`.

```{r}
penguins %>%
  rename(flipper_mm = flipper_length_mm)
```

####  **Practice Activity 2**

Starting with `penguins`, rename the `island` column to `island_name` and the `species` column to `penguin_spp`.

```{r}
penguins %>%
  rename(island_name = island,
         penguin_spp = species)
```

#### **Practice Activity 3**

Starting with `penguins`, convert any column names that start with “bill” to upper case.

```{r}
penguins %>%
  rename_with(toupper, starts_with("bill"))
```

## 7. Mutate()

####  **Practice Activity 1**

Add a column to `penguins` that contains a new column `flipper_m`, which is the `flipper_length_mm` (flipper length in millimeters) converted to units of meters.

```{r}
penguins %>%
  mutate(flipper_m = flipper_length_mm / 1000)
```

####  **Practice Activity 2**

The `year` column in `penguins` is currently an integer. Add a new column named `year_fct` that is the year converted to a factor (hint: `as.factor()`).

```{r}
penguins %>%
  mutate(year_fct = as.factor(year))
```

####  **Practice Activity 3**

To `penguins`, add a new column `mass_lb` that contains penguin body mass, currently in grams, converted to pounds (1 gram = 0.0022 lb).

```{r}
penguins %>%
  mutate(mass_lb = body_mass_g *.0022)
```

#### **Practice Activity 4**

Starting with `penguins`, do the following within a single `mutate()` function:

-   Convert the `species` variable to a character

-   Add a new column (called `flipper_cm` with flipper length in centimeters)

-   Convert the `island` column to lowercase

```{r}
penguins %>%
  mutate(species = as.character(species),
         flipper_cm = flipper_length_mm / 10,
         island = tolower(island))
```

## 8. **Group_by() %\>% summarize()**

####  **Practice Activity 1**

Starting with `penguins`, create a summary table containing the maximum and minimum length of flippers (call the columns `flip_max` and `flip_min`) for chinstrap penguins, grouped by island.

```{r}
penguins %>%
  
```

## 9. Across()

## 10. Count()

## 11. Case_when()
