---
title: "EDA Assignment Prep"
author: "Alex Greb"
format: html
editor: visual
---

## EDA Assignment Prep: Pokemon data

### Libraries

```{r}
library(here)
library(tidyverse)
library(janitor)
```

### Data

```{r}
pokedata <- read_csv(here("data/Pokemon.csv"))

pokedata <- pokedata %>% 
  clean_names()
```

### Describe the data: Pokemon

Data author: **Alberto Barradas**

[https://www.kaggle.com/datasets/abcsds/pokemon?resource=downloadhttps://www.kaggle.com/datasets/abcsds/pokemon?resource=download](https://www.kaggle.com/datasets/abcsds/pokemon?resource=download)

Description: This Pokemon data for 721 Pokemon and their stats

How many observations (rows) are there? 800

How many variables (columns) are there? 13

### skimr: Quick overview

```{r}
skim_data <- skimr::skim(pokedata)
```

### Summary: Quick overview

```{r}
summary(pokedata)
```

### Categorical vs. Continuous

```{r}
class(pokedata$number) # check class
pokedata$number <- as.factor(pokedata$number) # converts to factor
class(pokedata$number)
summary(pokedata$number)

summary(pokedata$type_1)
pokedata$type_1 <- as.factor(pokedata$type_1)
class(pokedata$type_1)
summary(pokedata$type_1)
```

How many categorical variables are there? 5 (maybe 6)

How many continuous variables are there? 7

What are some variables of interest to you?

------------------------------------------------------------------------

## EDA Assignment Prep: \[Insert Data Name Here\]

### Libraries

```{r}
library(here)
library(tidyverse)
library(janitor)
```

### Data

```{r}

```

### Describe the data:

Data author:

Description:

How many observations (rows) are there?

How many variables (columns) are there?

### Summary: Quick overview

```{r}

```

### Categorical vs. Continuous

```{r}

```

How many categorical variables are there?

How many continuous variables are there?

What are some variables of interest to you?
